---
title: "eds-212-day5-session1-qq"
format:
    html:
      code-fold: true
      code-summary: 'Show me the code!'
editor: visual
execute: 
  echo: true
  warning: false
---

```{r}
library(tidyverse)
```

# Explore Star Wars dataset

-   look at the first 6 lines of star wars

    ```{r}
    head(starwars)
    ```

-   find the dimensions of starwars

    ```{r}
    dim(starwars)
    ```

-   make a histogram of character heights

    ```{r}
    ggplot(data = starwars, aes(x = height)) + geom_histogram(fill = 'brown', color = 'white')
    ```

-   make a scatterplot of height vs weight

    ```{r}
    ggplot(data = starwars, aes(x = height, y = mass)) +
      geom_point(aes(color = gender))
    ```

## Calculate summary statistics

use mean() function to find means

use std() to find standard deviation

```{r}
mean_height <- mean(starwars$height, na.rm = TRUE)

mean_height
```

find and store SD of character heights:

```{r}
sd_height <- sd(starwars$height, na.rm = TRUE)
sd_height
```

## In-line reporting using code outputs

the mean height of star war characters is `r mean_height` cm with a standard deviation of 34.8 cm.
